Large-scale harmonic patterns clustering

### 2010-03-21 Paper/Paper.tex
improved

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.6\columnwidth]{code}
\end{center}
\caption{\small{A typical code from a codebook of size $200$. 
Patterns represented
$2$ bars and the pattern length was set to $16$.
BLACK AND WHITE VERSION COMING.
}}
\label{fig:code}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{close_patterns1}
\end{center}
\caption{\small{Cluster around some pattern... TO BE REDONE}}
\label{fig:cluster}
\end{figure}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{close_patterns_diff}
\end{center}
\caption{\small{Cluster around the pattern and the difference of both.}}
\label{fig:cluster_diff}
\end{figure}

@@

>>>>

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.6\columnwidth]{code}
\end{center}
\caption{\small{A typical code from a codebook of size $200$. 
Patterns represented
$2$ bars and the pattern length was set to $8$.
}}
\label{fig:code}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{close_patterns1}
\end{center}
\caption{\small{Cluster around centroid presented in
Figure \ref{fig:code}. Taken from the artist20 dataset, the cluster
size is actually $639$. Shown samples were randomly selected.
}}
\label{fig:cluster}
\end{figure}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{close_patterns_diff}
\end{center}
\caption{\small{First three patterns of figure \ref{fig:cluster}
($2$nd line) presented with the centroid from Figure \ref{fig:code}
($1$st line) and the difference between both ($3$rd line).
}}
\label{fig:cluster_diff}
\end{figure}

@@

The result presented here suggest a dynamic programming setting where
we could find the optimal bar segmentation according to our codebook. 
We could try
all possible bar length (in terms of beats) and not restrict ourselves
to $4$ beats bars and offsets between $0$ and $3$. This is part of
our future work.
